When talking about "Happy", I have three questions:

    1. How many types of happy do we normally get? 
    2. What kind of people would be much easier to feel happy?
    3. What can make us happy?
    
Then we can explore the data with these three questions bearing in mind.

### Step 0 - Load all the required libraries

From the packages' descriptions:

+ `tm` is a framework for text mining applications within R;
+ `tidyverse` is an opinionated collection of R packages designed for data science. All packages share an underlying design philosophy, grammar, and data structures;
+ `tidytext` allows text mining using 'dplyr', 'ggplot2', and other tidy tools;
+ `DT` provides an R interface to the JavaScript library DataTables.

```{r load libraries, warning=FALSE, message=FALSE}
library(tm)
library(tidytext)
library(tidyverse)
library(DT)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(RColorBrewer)
library(wordcloud)
```

### Step 1 - Load the data to be cleaned and processed

```{r read data, warning=FALSE, message=FALSE}
hm_data <- read_csv("/Users/Macbook/Downloads/HappyDB-master/happydb/data/cleaned_hm.csv")
demo.data <- read_csv("/Users/Macbook/Downloads/HappyDB-master/happydb/data/demographic.csv")
vad=read.csv("/Users/Macbook/Downloads/HappyDB-master/happydb/data/demographic.csv")
```

### Step 2 - Preliminary cleaning of text

We clean the text by converting all the letters to the lower case, and removing punctuation, numbers, empty words and extra white space.

```{r text processing in tm}
corpus <- VCorpus(VectorSource(hm_data$cleaned_hm))%>%
  tm_map(content_transformer(tolower))%>%
  tm_map(removePunctuation)%>%
  tm_map(removeNumbers)%>%
  tm_map(removeWords, character(0))%>%
  tm_map(stripWhitespace)
```

### Step 3 - Stemming words and converting tm object to tidy object

Stemming reduces a word to its word *stem*. We stem the words here and then convert the "tm" object to a "tidy" object for much faster processing.

```{r stemming}
stemmed <- tm_map(corpus, stemDocument) %>%
  tidy() %>%
  select(text)
```

### Step 4 - Creating tidy format of the dictionary to be used for completing stems

We also need a dictionary to look up the words corresponding to the stems.

```{r tidy dictionary}
dict <- tidy(corpus) %>%
  select(text) %>%
  unnest_tokens(dictionary, text)
```

### Step 5 - Removing stopwords that don't hold any significant information for our data set

We remove stopwords provided by the "tidytext" package and also add custom stopwords in context of our data.

```{r stopwords}
data("stop_words")
word <- c("happy","ago","yesterday","lot","today","months","month",
                 "happier","happiest","last","week","past")
stop_words <- stop_words %>%
  bind_rows(mutate(tibble(word), lexicon = "updated"))
```

### Step 6 - Combining stems and dictionary into the same tibble

Here we combine the stems and the dictionary into the same "tidy" object.

```{r tidy stems with dictionary}
completed <- stemmed %>%
  mutate(id = row_number()) %>%
  unnest_tokens(stems, text) %>%
  bind_cols(dict) %>%
  anti_join(stop_words, by = c("dictionary" = "word"))
```

### Step 7 - Stem completion

Lastly, we complete the stems by picking the corresponding word with the highest frequency.

```{r stem completion, warning=FALSE, message=FALSE}
completed <- completed %>%
  group_by(stems) %>%
  dplyr::count(dictionary, sort = TRUE) %>%
  mutate(word = dictionary[which.max(n)]) %>%
  ungroup() %>%
  select(stems, word) %>%
  distinct() %>%
  right_join(completed) %>%
  select(-stems)
```

### Step 8 - Pasting stem completed individual words into their respective happy moments

We want our processed words to resemble the structure of the original happy moments. So we paste the words together to form happy moments.

```{r reverse unnest}
completed <- completed %>%
  group_by(id) %>%
  summarise(text = str_c(word, collapse = " ")) %>%
  ungroup()
```


### Exporting the processed text data into a CSV file
```{r}
write_csv(hm_data, "/Users/Macbook/Downloads/HappyDB-master/happydb/data/processed_moments.csv")
```


## Merge with demographic data

```{r, echo= FALSE,message=FALSE, warning=FALSE}
hm_data <- hm_data %>%
  inner_join(demo.data, by = "wid") %>%
  select(wid,
         cleaned_hm,
         gender, 
         marital, 
         parenthood,
         reflection_period,
         age, 
         country, 
         predicted_category) %>%
  mutate(count = sapply(hm_data$cleaned_hm, wordcount)) %>%
  filter(gender %in% c("m", "f")) %>%
  filter(parenthood %in% c("n", "y")) %>%
  filter(reflection_period %in% c("24h", "3m")) %>%
  mutate(reflection_period = fct_recode(reflection_period, 
                                        months_3 = "3m", hours_24 = "24h"))
```

## Data Exploration

# Frequency of predicted category of happyniess
```{r}
category <- hm_data %>%
  dplyr::count(predicted_category, sort = TRUE)
category%>%
  mutate(predicted_category = reorder(predicted_category, n)) %>%
  ggplot(aes(predicted_category, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

# Frequency of happyniess lies in different marital conditions
```{r}
category <- hm_data %>%
  dplyr::count(marital, sort = TRUE)
category%>%
  mutate(marital = reorder(marital, n)) %>%
  ggplot(aes(marital, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

# Frequency of happyniess lies in different genders
```{r}
category <- hm_data %>%
  dplyr::count(gender, sort = TRUE)
category%>%
  mutate(gender = reorder(gender, n)) %>%
  ggplot(aes(gender, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

# Frequency of happyniess lies in different countries
```{r}
category <- hm_data %>%
  dplyr::count(country, sort = TRUE)
category%>%
  mutate(country = reorder(country, n)) %>%
  top_n(5, n) %>%
  ggplot(aes(country, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

# Frequency of happyniess lies in different parenthood conditions
```{r}
category <- hm_data %>%
  dplyr::count(parenthood, sort = TRUE)
category%>%
  mutate(parenthood = reorder(parenthood, n)) %>%
  ggplot(aes(parenthood, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

From the above visualization process, we can see that happynies would most likely happen to American who are single, with no parenthood and enjoy affection and achievement.


## Text analysis


# Identify the most popular words in each happy category.
```{r}
freq <- hm_data %>%
  select(wid,
         predicted_category, 
         cleaned_hm) %>%
  unnest_tokens(word, cleaned_hm) %>%
  anti_join(stop_words) %>% 
  dplyr::count(wid, word, sort = TRUE) %>%
  ungroup()

category <- hm_data %>%
  select(wid,
         predicted_category)

freq <- full_join(freq, category)


freq %>% 
  arrange(desc(n)) %>%
  group_by(predicted_category) %>%
  distinct(word, predicted_category, .keep_all = TRUE) %>%
  top_n(5, n) %>% 
  ungroup() %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  ggplot(aes(word, n, fill = predicted_category)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~predicted_category, ncol = 2, scales = "free") +
  coord_flip() +
  labs(title = "Most Popular Expressions in Each Happy Category",
       x = NULL, y = "Frequency")
```

The charts demonstrate the common expression in each category. 

```{r}
hm_data <- hm_data %>%
  unnest_tokens(word, cleaned_hm) %>%
  anti_join(stop_words)
hm_data <- hm_data %>%
  group_by(marital) %>%
  dplyr::count(word,sort= TRUE)
set.seed(0)
hm_data %>%
  acast(word ~ marital, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("hotpink2","limegreen"),
                   max.words = 100)
```


## Correlation between features

# Age group and oredicted happynies types
```{r}
ggplot(hm_data) +
  geom_bar(aes(x=age, fill=factor((predicted_category)))) +
  labs(fill="Predicted Happiness Categories") +
  scale_x_discrete(limits = seq(0,100,5)) +
  scale_y_discrete(limits=seq(0,100000,5000))
```
This chart demonstrates that younger people would be much easier to feel happy with things related to achievement and affection.

## Gender and Happiness Categories
```{r}
gen1 <- hm_data %>%
  group_by(gender) %>%
  dplyr::count(predicted_category)
set.seed(0)
gen1 %>%
  acast(predicted_category ~ gender, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("pink", "gray80"),
                   max.words = 100)
```

This wordcloud shows that the happyniess of male could be more related to achievement, bonding, leisure, and affection is enjoyed by both female and male.

## Parenthood and Happiness Categories

```{r}
gen1 <- hm_data %>%
  group_by(parenthood) %>%
  dplyr::count(predicted_category)
set.seed(0)
gen1 %>%
  acast(predicted_category ~ parenthood, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("limegreen", "black"),
                   max.words = 100)

```

This wordcloud demonstrates that the happyniess of people with no parenthood could be more related to achievement, bonding, leisure.

## Marital situations and Happiness Categories

```{r}
gen1 <- hm_data %>%
  group_by(marital) %>%
  dplyr::count(predicted_category)
set.seed(0)
gen1 %>%
  acast(predicted_category ~ marital, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("limegreen", "black"),
                   max.words = 100)
```

From this wordcloud, we can see that widowed are much easier to feel happy by bondings, which is consistent with common sense.
